---
title: "Analysis of Marriage Licenses in Toronto"
author: "Rayan Awad Alim"
thanks: "Code and data are available at: https://github.com/RayanAlim/marriage-statistical-analysis"
date: today
date-format: long
abstract: "This paper looks ar marriage license statistics in Toronto using data from the Toronto Open Data Portal."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse) 
library(ggplot2)
```

# Introduction

In this paper, we used Marriage License Data from the Toronto Open Data portal @opendatatoronto and anlaysed the data using @citeR.

# Data

The data is gathered from the Open Data Toronto portal and cleaned to include relevant fields. We explode the distribution of marriage licenses over time. The data is graphed in figure (@fig-marli). 

```{r}
#| label: fig-marli
#| fig-cap: Graph of Marriage Licences Over Time
#| echo: false
#| warning: false


cleaned_data <-
  read_csv(here::here("data/analysis_data/cleaned_marriage_licences.csv"))

ggplot(cleaned_data, aes(x = date, y = marriage_licenses, color = civic_centre)) +
  geom_line() +
  labs(title = "Marriage Licenses Over Time by Civic Centre", x = "Date", y = "Number of Licenses") +
  theme_minimal()
```

\newpage


# References


